Statically Typed String Sanitation Inside a Python

### 2014-08-06 sanitation-psp14/sanitation-psp14-short.tex
typos

Unlike \emph{frameworks and libraries} provided by languages such as Haskell and Ruby, our type system provides a \emph{static} guarantee that input is always properly sanitized before use. Doing so requires reasoning about the operations on regular languages corresponding to standard operations on strings; we are unaware of any production system which contains this form of reasoning. Therefore, even where frameworks and libraries provide a viable interface or wrapper around input sanitation, our approach is complementary because it ensurees the correctness of the framework or library itself. Furthermore, our approach is more general than database abstraction layers because our mechanism is applicable to all forms of command injection (e.g. shell injection or remote file inclusion).

>>>>

Unlike \emph{frameworks and libraries} provided by languages such as Haskell and Ruby, our type system provides a \emph{static} guarantee that input is always properly sanitized before use. Doing so requires reasoning about the operations on regular languages corresponding to standard operations on strings; we are unaware of any production system which contains this form of reasoning. Therefore, even where frameworks and libraries provide a viable interface or wrapper around input sanitation, our approach is complementary because it ensures the correctness of the framework or library itself. Furthermore, our approach is more general than database abstraction layers because our mechanism is applicable to all forms of command injection (e.g. shell injection or remote file inclusion).
